Review stages

### 2024-05-17 doc/review-stages.qmd
build: setup targets for getting the abstracts

```{r}
targets::tar_read(titles_selected) |> 
  dplyr::pull(id) |> 
  openalex_retrieve_abstracts() |>
  jsonlite::toJSON() |> 
  jsonlite::parse_json() |>
  yaml::as.yaml() |>
  yaml::write_yaml(here("data/review/abstracts.yaml"))
```

@@

-   first skimming the papers and group by themes
-   then read a few from each theme to decide on what information to
    extract
-   then discuss together the themes to group by and information to
    extract
-   then we follow what we agreed on

>>>>

@@

-   first skimming the papers and group by themes, writing a basic
    free-hand summary
-   then read a few from each theme to decide on what information to
    extract
-   then discuss together the themes to group by and information to
    extract
-   then we follow what we agreed on
